\documentclass[document.tex]{subfiles}
\begin{document}

\chapter{Post-doc Meeting 2023 March 15-17}
\label{day:2023-03-15}

\section*{Thursday 16th}

    \subsection{PCR, Policy and Pandemics: A Science Journey
    Keynote Speaker : Mike Bunce - Chief Science Advisor, DOC}
    \begin{itemize}
    \item Linking research to policy 
    \item Genomics has yet to intergrate into gov industries 
    \item Team science - communication with non-geneticists and supporting other fields of science
    \item Flexibility - follow paths available, where is the momentem in the field  
    \item Be selective with collab
    \item Data accessibility and transparency, what do non-scientists want to know/see 
    \item Intergrating a narrative into your CV. What have you acheived? Who are the consumers of your science? community impact. venom-fisheries-genome evolution-parasites/human health-conservation-rat race evolution ~ write an article for a community newletter/blog/fbpage/twitter about invasive species and activity by scientist to protect our environment. how to eliminate an invasive species?  
    \item Rat race science vs invasive species. how can we get the winning edge?
    \item comic strip 
    \item 
    \end{itemize}

    \subsection{Bioinformatics Workshops: How to build a workshop Mik Black and Tyler McInnes}
    \begin{itemize}
    \item 
    \item 
    \end{itemize}

    \subsection{How to Build a Post-doc Life with early/established career researchers/Anna Santure - Having Fun with the Extras/Libby Liggins - Do Look Up}
    \begin{itemize}
    \item Setting boundries and expectations with post grad students from the outset
    \item 
    \item 
    \end{itemize}

    \subsection{Keynote Speaker : Jude Sise – Consultant, AbacusBio (via Zoom)}
    \begin{itemize}
    \item 
    \item 
    \end{itemize}

    \subsection{Create and Take Opportunities - Make Your Own Luck Keynote Speaker: Julie Everett-Hincks - Principal Analyst, MfE}
    \begin{itemize}
    \item RSNZ GE panel
    \item 
    \end{itemize}

    \subsection{Workshop: Bioinformatics best practices Mik Black and Jian Sheng Boey}
    \begin{itemize}
    \item 
    \item 
    \end{itemize}



\section*{Friday 17th}

    \subsection{Cultural Competency at the University of Otago - Auckland Centre Tracey Godfery—GA Vision Mātauranga Manager}
    \begin{itemize}
    \item 
    \item 
    \end{itemize}
    
    \subsection{Media Training at the Auckland Univers}
    \begin{itemize}
    \item inflection
    \item 
    \item 
    \end{itemize}
    
    
\bib{}
    \end{document}